---
title: "TidyTemplate"
date: 2020-10-13
output:
  html_document: 
    toc: yes
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: true
    keep_md: yes
    code_download: yes
editor_options:
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that data set, and ask you to explore the data.
While the data-set will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of Tidy Tuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(tidytuesdayR)
library(tidymodels)
library(gganimate)

```

```{r echo=FALSE}
theme_roboto <- function(base_size = 11,
                         strip_text_size = 12,
                         strip_text_margin = 5,
                         subtitle_size = 13,
                         subtitle_margin = 10,
                         plot_title_size = 16,
                         plot_title_margin = 10,
                         ...) {
    ret <- ggplot2::theme_minimal(base_family = "RobotoCondensed-Regular",
                                  base_size = base_size, ...)
    ret$strip.text <- ggplot2::element_text(
        hjust = 0, size = strip_text_size,
        margin = ggplot2::margin(b = strip_text_margin),
        family = "Roboto-Bold"
    )
    ret$plot.subtitle <- ggplot2::element_text(
        hjust = 0, size = subtitle_size,
        margin = ggplot2::margin(b = subtitle_margin),
        family = "RobotoCondensed-Regular"
    )
    ret$plot.title <- ggplot2::element_text(
        hjust = 0, size = plot_title_size,
        margin = ggplot2::margin(b = plot_title_margin),
        family = "Roboto-Bold"
    )
    ret
}
#from: https://github.com/juliasilge/silgelib/blob/master/R/graphing.R
```



# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

#tt <- tt_load("2020-10-13") # Limited Exceeded
datasaurus <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-10-13/datasaurus.csv')

```


# Readme

Take a look at the readme for the weekly data to get insight on the data-set.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

# tt
datasaurus
```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

# tt %>% 
#   map(glimpse)

datasaurus %>% glimpse()

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each data-set by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

#datasaurus <- tt$datasaurus
datasaurus <- datasaurus %>% mutate(dataset = factor(dataset))

datasaurus %>% 
  group_by(dataset) %>% 
  summarise(across(c(x,y), 
                   list(mean = mean,
                        sd = sd)),
            x_y_cor = cor(x,y),
            count = n())%>% 
  kableExtra::kable(caption = "Similarities for X and Y in each dataset") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

datasaurus %>% 
  group_by(dataset) %>% 
  summarise(across(c(x,y), 
                   list(min = min,
                        max = max)
                   ))%>% 
  kableExtra::kable(caption = "Differences for X and Y in each dataset") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize_Animate}

datasaurus %>% 
  ggplot(aes(x=x, y=y)) +
  geom_point(alpha=0.7) +
  theme_light() +
  theme_roboto()+
  ggtitle('Now showing {closest_state}') +
  transition_states(dataset,
                    transition_length = 2,
                    state_length = 3)


  
```


```{r Visualize_Static}

datasaurus %>% 
  ggplot(aes(x=x, y=y, color=dataset)) +
  geom_point(alpha=0.7) +
  theme_light() +
  facet_wrap(~dataset)+
  theme_roboto()
  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r Saving_Image}

# This will save your most recent plot
ggsave(
  filename = "DatasauRus.png",
  device = "png")

```


# Can we predict which dataset a point belongs too?
+ The size of the datasate will make harder to get a good result.

## Build a model
```{r Build_Model}
set.seed(332)
# Using K-Folds
dino_folds <- datasaurus %>% 
  bootstraps()

rf_spec <- rand_forest(trees = 1000) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")

dino_wf <- workflow() %>% 
  add_model(rf_spec) %>% 
  add_formula(dataset ~ x+y)

doParallel::registerDoParallel()

dino_rs <- fit_resamples(
  dino_wf,
  resamples = dino_folds,
  control = control_resamples(save_pred = TRUE)
)
```


## Evaluate model

```{r Metrics}
collect_metrics(dino_rs)  %>%
kableExtra::kable(caption = "How good is the model?") %>%
kableExtra::kable_styling(bootstrap_options = "striped")
```

```{r Names}
dino_pred <- dino_rs %>% 
  collect_predictions()

dino_pred %>% names()
```


```{r PPV_Metrics}
dino_pred %>%
  group_by(id) %>%
  ppv(dataset, .pred_class) #Prediction Positive Values
```

### ROC Curves
```{r ROC, fig.height = 11, fig.width = 11}
dino_pred %>%
  group_by(id) %>%
  roc_curve(dataset, .pred_away:.pred_x_shape) %>%
  ggplot(aes(1-specificity, sensitivity, color=id)) +
  geom_abline(lty=2, color="gray80", size=1.5) +
  geom_path(show.legend = FALSE, alpha=0.7, size=1) +
  facet_wrap(~.level, ncol=4) +
  coord_equal() +
  theme_roboto()
```

+ The model's predictive power varies with the datasets.
+ The model is good to predict the datasets: dots, h_lines, and v_lines.
+ The model is almost guessing for the datasets dino and away.


### Confusion matrix

```{r Conf_Matrix, fig.height = 6, fig.width = 11}
dino_pred %>% 
  conf_mat(dataset, .pred_class) %>% 
  autoplot(type="heatmap")+
  theme_roboto()+
  scale_fill_gradient2(low = "grey80",
                      mid = "grey80",
                      high = "orange",
                      midpoint = 0,
                      space = "Lab",
                      na.value = "grey80",
                      guide = FALSE,
                      aesthetics = "fill")
```

+ Excluding the right cases
```{r Conf_Matrix_False, fig.height = 6, fig.width = 11}
dino_pred %>% 
  filter(.pred_class != dataset) %>% 
  conf_mat(dataset, .pred_class) %>% 
  autoplot(type="heatmap")+
  theme_roboto()+
  scale_fill_gradient2(low = "grey80",
                        mid = "grey80",
                        high = "orange",
                        midpoint = 0,
                        space = "Lab",
                        na.value = "grey80",
                        guide = FALSE,
                        aesthetics = "fill")
```
