---
title: "TidyTemplate"
date: 2020-11-03
output:
  html_document: 
    code_download: yes
    fig_height: 9
    fig_width: 12
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_collapsed: yes
    toc_float: yes
editor_options:
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidytuesdayR)
library(tidyverse)
library(scales)
library(skimr)
library(magrittr)
library(forcats)
library(glue)
library(ggridges)
```

```{r echo=FALSE}
theme_roboto <- function(base_size = 11,
                         strip_text_size = 12,
                         strip_text_margin = 5,
                         subtitle_size = 13,
                         subtitle_margin = 10,
                         plot_title_size = 16,
                         plot_title_margin = 10,
                         ...) {
  ret <- theme_minimal(base_family = "RobotoCondensed-Regular",
                       base_size = base_size, 
                       ...)
  
  ret$strip.text <- element_text(hjust = 0, 
                                 size = strip_text_size,
                                 margin = ggplot2::margin(b = strip_text_margin),
                                 family = "Roboto-Bold",
                                 color = "#003399")
  
  ret$plot.subtitle <- element_text(hjust = 0, 
                                    size = subtitle_size,
                                    margin = ggplot2::margin(b = subtitle_margin),
                                    family = "RobotoCondensed-Regular",
                                    color = "#003399")
  
  ret$plot.title <- element_text(hjust = 0, 
                                 size = plot_title_size,
                                 margin = ggplot2::margin(b = plot_title_margin),
                                 family = "Roboto-Bold",
                                 face = "bold",
                                 color = "#003399")
  
  ret$plot.background = element_rect(fill = "#ffcc00")
  
  ret$axis.text = element_text(color = "#003399")
  
  ret$axis.title = element_text(color = "#003399",
                                family = "Roboto-Bold",
                                face = "bold")
  ret$panel.grid.major = element_line(size = 0.3, 
                                      linetype = 'solid', 
                                      color = "white") 
  
  ret$panel.grid.minor = element_line(size = 0.2, 
                                      linetype = 'solid', 
                                      colour = "white")
  
  ret$plot.caption = element_text(hjust = 1, 
                                  family = "RobotoCondensed-Regular", 
                                  color = "#003399")
  
  ret
}

```
# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load, message=FALSE}

tt <- tt_load("2020-11-03")

# Caption text
caption_text = expression(paste(italic("Data source: "), 
                                bold("Ikea "), 
                                italic("& "), 
                                bold("Kaggle"), 
                                italic(" | Graphic: "), 
                                bold("Renato Albolea")))
```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

ikea <- tt$ikea %>% 
  select(-X1)

ikea %>% skim()

ikea %<>% 
  add_count(category, name="category_count") %>% 
  mutate(old_price = parse_number(if_else(old_price=='No old price', 
                                          as.character(price), 
                                          str_remove(old_price, "SR "))),
         promotion = old_price!=price,
         discount = old_price - price,
         discount_perc = discount/old_price,
         category = str_trim(str_remove(category, 'furniture')) ,
         category_num = glue("{category}(#{category_count})"),
         name = fct_lump(name, 20),
         short_description = str_trim(str_squish(short_description)),
         volume = depth*width*height/10^6) 

ikea %<>%separate(short_description,
                  into = c("main_description", "rest"),
                  sep = ", ",
                  extra = "merge",
                  fill = "right",
                  remove = FALSE)

ikea %<>% extract(col = rest,
                  into = "description_size",
                  regex = "([\\d\\-xX]+)",
                  remove = FALSE)
  
```

+ No missing data
+ `r round(mean(ikea$sellable_online)*100,2)`% of the products are sellable online.


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
ikea %>% 
  count(category, sort = TRUE) %>% 
  ggplot(aes(x=n,
             y = fct_reorder(category, n))) +
  geom_col(fill = "#003399") + 
  theme_roboto()+
  labs(title = "Ikea product distribution",
       x = "Number of items",
       y = element_blank(),
       caption = caption_text)
```


```{r Discount}
ikea %>% 
  filter(promotion) %>% 
  ggplot(aes(x=discount_perc,
             y=fct_reorder(category, discount_perc, .fun='mean'))) + 
  geom_boxplot() +
  theme_roboto() +
  labs(title = "Trolleys is the most discounted item",
       x = "Discount Percentage",
       y = element_blank(),
       caption = caption_text) + 
  scale_x_continuous(labels=percent)
```

```{r Discount_2}
ikea %>% 
  filter(promotion) %>% 
  ggplot(aes(x=discount_perc,
             y=fct_reorder(category_num, discount_perc, .fun='mean'))) + 
  geom_density_ridges(fill = "#003399",
                      alpha = 0.8) +
  theme_roboto() +
  labs(title = "Trolleys is the most discounted item",
       x = "Discount Percentage",
       y = element_blank(),
       caption = caption_text) + 
  scale_x_continuous(labels=percent)
```

```{r Price}
ikea %>% 
  ggplot(aes(x=price,
             y=fct_reorder(category_num, price, .fun='mean'))) + 
  geom_boxplot() +
  theme_roboto() +
  labs(title = "On average, Wardrobes is the most expensive item",
       x = "Price in SR$",
       y = element_blank(),
       caption = caption_text) +
  scale_x_log10(labels=dollar)

```

```{r Price_2}
ikea %>% 
  ggplot(aes(x=price,
             y=fct_reorder(category_num, price, .fun='mean'))) + 
  geom_density_ridges(fill = "#003399",
                      alpha = 0.8) +
  theme_roboto() +
  labs(title = "On average, Wardrobes is the most expensive item",
       x = "Price in SR$",
       y = element_blank(),
       caption = caption_text) +
  scale_x_log10(labels=dollar)

```

# Does having option of color influence the price?

```{r}
ikea %>% 
  filter(promotion) %>% 
  ggplot(aes(x=discount_perc,
             y=fct_reorder(category_num, discount_perc, .fun='mean'),
             fill = other_colors)) + 
  geom_boxplot() +
  theme_roboto() +
  labs(title = "Trolleys is the most discounted item",
       x = "Discount Percentage",
       y = element_blank(),
       caption = caption_text) + 
  scale_x_continuous(labels=percent)
```

```{r}
ikea %>% 
  filter(promotion) %>% 
  ggplot(aes(x=discount_perc,
             y=fct_reorder(category_num, discount_perc, .fun='mean'),
             fill = other_colors)) + 
  geom_density_ridges(alpha = 0.8) +
  theme_roboto() +
  labs(title = "Trolleys is the most discounted item",
       x = "Discount Percentage",
       y = element_blank(),
       caption = caption_text) + 
  scale_x_continuous(labels=percent)
```

```{r}
ikea %>% 
  ggplot(aes(x=price,
             y=fct_reorder(category_num, price, .fun='mean'),
             fill = other_colors)) + 
  geom_boxplot() +
  theme_roboto() +
  labs(title = "On average, Wardrobes is the most expensive item",
       x = "Price in SR$",
       y = element_blank(),
       caption = caption_text) +
  scale_x_log10(labels=dollar)

```

```{r}
ikea %>% 
  ggplot(aes(x=price,
             y=fct_reorder(category_num, price, .fun='mean'),
             fill = other_colors)) + 
  geom_density_ridges(alpha = 0.8) +
  theme_roboto() +
  labs(title = "On average, Wardrobes is the most expensive item",
       x = "Price in SR$",
       y = element_blank(),
       caption = caption_text) +
  scale_x_log10(labels=dollar)

```

+ For some categories we can see price difference for having color options.
+ Bar and Trolley have a different behaviour. Only cheapper products offer color options.

# How well organized is the products?

```{r}
ikea %>% 
  count(name, category) %>% 
  filter(name != "Other") %>% 
  ggplot(aes(x=n,
             y=fct_reorder(name, n, sum) ,
             fill= fct_reorder(category, n, sum))) +
  geom_col() +
  theme_roboto() +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE),
                      name = "Category") +
  labs(title = "The client cannot look to the name to have simmilar design accros categories",
       subtitle = "Few product names are used in the company",
       x = "Number of items",
       y = element_blank(),
       caption = caption_text) 
  
```

# Volume distribution

```{r}
ikea %>% 
  filter(!is.na(volume),
          volume > 0.01) %>% 
  arrange(desc(volume)) %>% 
  add_count(category, name = "category_count") %>% 
  mutate(category_num = glue("{category}(#{category_count})"),
         category_num = fct_reorder(category_num, volume, .fun='mean')) %>% 
  ggplot(aes(volume, category_num)) +
  geom_boxplot() +
  scale_x_log10() +
  theme_roboto() +
    labs(title = "As expected, sofas and wardrobes are the bigest items",
       subtitle = "",
       x = "Volume in m^3",
       y = element_blank(),
       caption = caption_text) 
```

# Is there any relationship between price and volume?

```{r}
ikea %>% 
  filter(!is.na(volume),
          volume > 0.01) %>%
  mutate(category = fct_lump(category, 8)) %>% 
  add_count(category, name = "category_count") %>% 
  mutate(category_num = glue("{category}(#{category_count})"),
         category_num = fct_reorder(category_num, volume, .fun='mean'),
         ) %>% 
  ggplot(aes(price, volume)) + 
  geom_point() +
  geom_smooth(method="lm") +
  facet_wrap(~category) +
  theme_roboto() +
    labs(title = "The graph shows some relationship, but not completly linear",
       subtitle = "",
       x = "Volume in m^3",
       y = element_blank(),
       caption = caption_text) 


```


```{r}
ikea %>% 
  filter(!is.na(volume),
          volume > 0.01) %>%
  mutate(category = fct_lump(category, 8)) %>% 
  add_count(category, name = "category_count") %>% 
  mutate(category_num = glue("{category}(#{category_count})"),
         category_num = fct_reorder(category_num, volume, .fun='mean'),
         ) %>% 
  ggplot(aes(price, volume)) + 
  geom_point() +
  geom_smooth(method="lm") +
  facet_wrap(~category) +
  scale_x_log10() +
  scale_y_log10() +
  theme_roboto() +
    labs(title = "The relationship seems strong after the log transformation",
       subtitle = "",
       x = "Volume in m^3",
       y = element_blank(),
       caption = caption_text) 


```

```{r}
ikea %>% 
  filter(!is.na(volume),
          volume > 0.01) %>%
  add_count(category, name = "category_count") %>% 
  mutate(category_num = glue("{category}(#{category_count})")) %>%
  group_by(category_num) %>% 
  summarise(price_vol_cor = round(cor(price,volume), 3),
            log_price_log_vol_cor = round(cor(log2(price), log2(volume)),3)) %>% 
  arrange(-log_price_log_vol_cor) %>% 
  kableExtra::kable(caption = "Corelation between price and volume") %>% 
  kableExtra::kable_styling(bootstrap_options = "striped")
  
```


# Main factors that influences the price

```{r}
library(broom)
ikea %>% 
  filter(!is.na(volume),
          volume > 0.01) %>%
  mutate(category = fct_lump(category, 16),
         category_num = glue("{category}(#{category_count})"),
         category_num = fct_relevel(category_num, "Tables & desks(#612)"))%>% 
  add_count(category, name="category_count") %>% 
  lm(log2(price) ~ log2(volume) + category_num + other_colors, data = .) %>% 
  tidy(conf.int = TRUE) %>% 
  filter(term != "(Intercept)") %>% 
  mutate(term = ifelse(term == "log2(volume)", "Volume(doubling)", term),
         term = str_remove_all(term, "category_num"),
         term = fct_reorder(term, estimate)) %>% 
  ggplot(aes(estimate, term)) +
  geom_point() + 
  geom_errorbarh(aes(xmin = conf.low, xmax=conf.high), height=0.15, color = "#003399") +
  geom_vline(xintercept = 0, color = "#003399", lty=2 ) +
  theme_roboto() +
  xlim(-2,2)+
  theme_roboto() +
    labs(title = "Volume is a major contributor to price",
       subtitle = "",
       x = "Impact on price.\n Base Case: Tables & desk with no other color",
       y = element_blank(),
       caption = caption_text) 
```

